### 2021-03-29 papers.tex
Introduce some rudimentary badges
Still need to add them to papers and figure out how to put them at the
top of the page

\addtrack
    {}{Fun(?) and Games Track}
\addpaper
    {Back to Square One: Superhuman Performance in Chutes and Ladders Through Deep Neural Networks and Tree Search}
    {Dylan R. Ashley, Anssi Kanervisto and Brendan Bennett}
    {Keywords: Almost Monopoly, AlphaX, Artificial Neural Networks, Board Games, Deep Learning, Games With Boards, Machine Learning, Machine Learning That Matters, Reinforcement Learning, Tree Search}
    {SIGBOVIK_2021_paper_5}
    {0cm}
    {}
\addpaper
    {Demystifying the Mortal Kombat Song}
    {J Devi and Chai-Tea Latte}
    {Keywords: mortal-kombat, truth, meaning-of-life}
    {SIGBOVIK_2021_paper_12}
    {0cm}
    {}
\addpaper
    {Unicode Magic Tricks}
    {Nicolas Hurtubise}
    {Keywords: Unicode, magic trick, emojis, bitwise operators, sleight of bits}
    {SIGBOVIK_2021_paper_13}
    {0cm}
    {}
\addpaper
    {Video games in Fonts Fontemon}
    {Michael Mulet}
    {Keywords: font, video game, font video game, silly idea done seriously}
    {SIGBOVIK_2021_paper_18}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_5}
    {0cm}

>>>>

\addtrack
    {}{Fun(?) and Games Track}
\addpaper
    [fancy]
    [\badge{unavailable}\badge{unusable}\badge{pagenumbers}]
    {Back to Square One: Superhuman Performance in Chutes and Ladders Through Deep Neural Networks and Tree Search}
    {Dylan R. Ashley, Anssi Kanervisto and Brendan Bennett}
    {Keywords: Almost Monopoly, AlphaX, Artificial Neural Networks, Board Games, Deep Learning, Games With Boards, Machine Learning, Machine Learning That Matters, Reinforcement Learning, Tree Search}
    {SIGBOVIK_2021_paper_5}
    {0cm}
    {}
\addpaper
    {Demystifying the Mortal Kombat Song}
    {J Devi and Chai-Tea Latte}
    {Keywords: mortal-kombat, truth, meaning-of-life}
    {SIGBOVIK_2021_paper_12}
    {0cm}
    {}
\addpaper
    {Unicode Magic Tricks}
    {Nicolas Hurtubise}
    {Keywords: Unicode, magic trick, emojis, bitwise operators, sleight of bits}
    {SIGBOVIK_2021_paper_13}
    {0cm}
    {}
\addpaper
    {Video games in Fonts Fontemon}
    {Michael Mulet}
    {Keywords: font, video game, font video game, silly idea done seriously}
    {SIGBOVIK_2021_paper_18}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_5}
    {0cm}
